Xor-Some Preregistered Study: Analyses

### 2022-04-17 analysis/main/01_xor-some_prereg_preprocessing_final.Rmd
fix analyses and plots with correctly z-scored data

# apply exclusion criteria to main trials
# check range of responses per participant
d_main_fail <- d_main %>% group_by(submission_id) %>%
  mutate(passed_main = case_when(max(response) - min(response) <= 10 ~ FALSE,
                                 TRUE ~ TRUE)
         ) %>% filter(passed_main == F)
# now check for critical trials only
d_main_critical_fail <- d_main %>% group_by(submission_id) %>% 
  filter(condition == "critical") %>%
  mutate(passed_main = case_when(max(response) - min(response) <= 10 ~ FALSE,
                                 TRUE ~ TRUE)
         ) %>% filter(passed_main == F)
# now check implicature trials only 
d_main_implicature_fail <- d_main %>% group_by(submission_id) %>% 
  filter((block == "xor") | (block == "some")) %>%
  mutate(passed_main = case_when(max(response) - min(response) <= 10 ~ FALSE,
                                 TRUE ~ TRUE)
         ) %>% filter(passed_main == F)
# check if this failure is the case for certain vignettes more often then for others
d_main_implicature_fail %>% ungroup() %>% group_by(ID, block) %>% count() %>% View()
# --> it seems that the vignettes 28 (xor) and 45 (some) have this issue the most
# check how often the single participants do this
d_main_implicature_fail %>% count() %>% View()
# --> all of them do this on all of the trials - these are 15 people 
# write out a csv with their IDs for an exploratory exclusion
#d_main_implicature_fail %>% count() %>% write_csv("./../../data/main/submission-ids_implicature_fails.csv")

@@

@@

Write out z-scored data:
```{r}
d_critical_zScored %>% write_csv("./../../data/main/results_prereg_tidy_final_zScored_long.csv")
d_critical_zScored_wide %>% write_csv("./../../data/main/results_prereg_tidy_final_zScored_wide.csv")
d_critical_noDuplicates_zScored %>% write_csv("./../../data/main/results_prereg_tidy_noDuplicates_zScored_long.csv")

>>>>

# apply exclusion criteria to main trials
# check range of responses per participant
d_main_fail <- d_main %>% group_by(submission_id) %>%
  mutate(passed_main = case_when(max(response) - min(response) <= 10 ~ FALSE,
                                 TRUE ~ TRUE)
         ) %>% filter(passed_main == F)
# now check for critical trials only
d_main_critical_fail <- d_main %>% group_by(submission_id) %>% 
  filter(condition == "critical") %>%
  mutate(passed_main = case_when(max(response) - min(response) <= 10 ~ FALSE,
                                 TRUE ~ TRUE)
         ) %>% filter(passed_main == F)
# now check implicature trials only 
d_main_implicature_fail <- d_main %>% group_by(submission_id) %>% 
  filter((block == "xor") | (block == "some")) %>%
  mutate(passed_main = case_when(max(response) - min(response) <= 10 ~ FALSE,
                                 TRUE ~ TRUE)
         ) %>% filter(passed_main == F)
# check if this failure is the case for certain vignettes more often then for others
d_main_implicature_fail %>% ungroup() %>% group_by(ID, block) %>% count() %>% arrange(., desc(n)) # View()
# --> it seems that the vignettes 28 (xor) and 45 (some) have this issue the most
# check how often the single participants do this
d_main_implicature_fail %>% count() # %>% View()
# --> all of them do this on all of the trials - these are 15 people 
# write out a csv with their IDs for an exploratory exclusion
#d_main_implicature_fail %>% count() %>% write_csv("./../../data/main/submission-ids_implicature_fails.csv")

@@

d_critical_noDuplicates_zScored_wide <- d_critical_noDuplicates_zScored %>% 
  select(submission_id, title, main_type, block_extended, response_centered) %>% 
  unique() %>% 
  pivot_wider(
    names_from = block_extended, 
    values_from = response_centered, 
    values_fn = mean # getting means for double prior measurement in "xor"
  ) 
```

Z-score data when excluding participants who failed the implicature ratings: 
```{r}
d_critical_clean_noImplFails <- d_clean_exclude_implicatureFails %>% filter(condition == "critical")
d_critical_long_noImplFails <- d_critical_clean_noImplFails %>% 
  pivot_longer(c(competence, relevance, prior), 
               names_to = "class_condition", 
               values_to = "prior_class")

d_critical_long_noImplFails <- d_critical_long_noImplFails %>% 
  mutate(block = ifelse(block == "comp", "competence", 
                        ifelse(block == "rel", "relevance", ifelse(block == "pri", "prior", block) )))

d_critical_long_noImplFails <- d_critical_long_noImplFails %>% 
  mutate(
    block_extended =  ifelse(block %in% c("some", "xor"), "target", block)
  )

# z-scoring, excluding duplicates
d_critical_zScored_noImplFails_noDuplicates <- d_critical_long_noImplFails %>% 
  filter((block_extended == class_condition) | (class_condition =="relevance" & block_extended == "target") )

d_critical_noImplFails_noDuplicates_zScored <- d_critical_zScored_noImplFails_noDuplicates %>% group_by(submission_id, block_extended) %>%
  mutate(block_mean = mean(response),
         block_sd = sd(response),
         response_centered = (response - block_mean)/block_sd,
         # catch the cases where sd is 0 
         response_centered = ifelse(is.na(response_centered), 0, response_centered))

d_critical_noImplFails_noDuplicates_zScored_wide <- d_critical_noImplFails_noDuplicates_zScored %>% 
  select(submission_id, title, main_type, block_extended, response_centered) %>% 
  unique() %>% 
  pivot_wider(
    names_from = block_extended, 
    values_from = response_centered, 
    values_fn = mean # getting means for double prior measurement in "xor"
  ) 
```

@@

Write out z-scored data:
```{r}
d_critical_zScored %>% write_csv("./../../data/main/results_prereg_tidy_final_zScored_long.csv")
d_critical_zScored_wide %>% write_csv("./../../data/main/results_prereg_tidy_final_zScored_wide.csv")
d_critical_noDuplicates_zScored %>% write_csv("./../../data/main/results_prereg_tidy_noDuplicates_zScored_long.csv")
d_critical_noDuplicates_zScored_wide %>% write_csv("./../../data/main/results_prereg_tidy_noDuplicates_zScored_wide.csv")
d_critical_noImplFails_noDuplicates_zScored %>%
  write_csv("./../../data/main/results_prereg_tidy_noDuplicates_noImplFails_zScored_long.csv")
d_critical_noImplFails_noDuplicates_zScored_wide %>%
  write_csv("./../../data/main/results_prereg_tidy_noDuplicates_noImplFails_zScored_wide.csv")

### 2022-04-17 analysis/main/02_xor-some_prereg_plots_final.Rmd
fix analyses and plots with correctly z-scored data

Read data created in preprocessing script:
```{r, warning=FALSE, message=FALSE, results='hide'}
d_critical_zScored_wide <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide.csv")
d_critical_zScored <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_long.csv")
d_test <- read_csv("./../../data/main/results_prereg_raw_final_test.csv")
d_critical_zScored_wide_xor_priors_order <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide_xor_priors-order.csv")
d_critical_zScored_wide_xor_priors_type <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide_xor_priors-type.csv")
```

@@

ggsave("../../writing/ELM2/byItem-scatter-wTitles.pdf", width = 9, height = 7)

@@

ggsave("../../writing/ELM2/byFactor-byPrior-raw-scatter.pdf", width = 9, height = 7)
```

>>>>

Read data created in preprocessing script:
```{r, warning=FALSE, message=FALSE, results='hide'}
d_critical_zScored_wide <- read_csv("./../../data/main/results_prereg_tidy_noDuplicates_zScored_wide.csv")
#d_critical_zScored_wide <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide.csv")
d_critical_zScored <- read_csv("./../../data/main/results_prereg_tidy_noDuplicates_zScored_long.csv")
#d_critical_zScored <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_long.csv")
d_test <- read_csv("./../../data/main/results_prereg_raw_final_test.csv")
d_critical_zScored_wide_xor_priors_order <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide_xor_priors-order.csv")
d_critical_zScored_wide_xor_priors_type <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide_xor_priors-type.csv")
```

@@

#ggsave("../../writing/ELM2/byItem-scatter-wTitles.pdf", width = 9, height = 7)

@@

#ggsave("../../writing/ELM2/byFactor-byPrior-raw-scatter.pdf", width = 9, height = 7)
```

### Simulated plots for the paper

Below, some simulations are conducted to create plots for the paper.

### 2022-04-17 analysis/main/03_xor-some_prereg_analysis_final.Rmd
fix analyses and plots with correctly z-scored data

@@

@@

The binary test of conformity with the theoretical predictions therefore is:
```{r}
test_conjunction_of_all_hypotheses <-  function(posterior_hypotheses) {
  posterior_hypotheses %>% 
    mutate(hypothesis_true = case_when(
      key == 'competence_some' ~ positive_eff > 0.95,
      key == 'competence_xor'  ~ positive_eff > 0.95,
      key == 'prior_some' ~ negative_eff > 0.95,
      key == 'prior_xor'  ~ negative_eff > 0.95, 
      key == 'relevance_some' ~ positive_eff > 0.95,
      key == 'relevance_xor'  ~ positive_eff > 0.95
    )) %>% 
    pull(hypothesis_true) %>% all()
}
# applied to the pilot data
test_conjunction_of_all_hypotheses(posterior_hypotheses)
```
### Plot posterior distributions

```{r, fig.height = 6, fig.width=9}
model_SI_posteriors %>% select(prior_xor, prior_some,
                               competence_xor, competence_some,
                               relevance_xor, relevance_some) %>%
  pivot_longer(cols = everything(), names_to = "effect", values_to = "value") -> model_SI_posteriors_long

@@

# ggsave("../../writing/ELM2/posterior-effects.pdf", width=7, height=5)
```

@@

Model with binary predictors:
```{r, results='hide', message=FALSE, warning=FALSE}
d_critical_zScored %>% 
  select(submission_id, title, main_type, block_extended, response_centered, prior_class, class_condition) %>% 
  unique() %>% 
  pivot_wider(
    names_from = class_condition, 
    values_from = prior_class
  )  %>%
  mutate(relevance = factor(relevance, levels = c(1, 0)),
         competence = factor(competence, levels = c(1, 0)),
         prior = factor(prior, levels = c(1, 0)),
         main_type = as.factor(main_type)) %>% 
  filter(block_extended == "target") -> d_critical_wide_cat_zScored
# sum code predictors
# low prior: -1, high prior:: 1 
contrasts(d_critical_wide_cat_zScored$prior) <- contr.sum(2)
# low comp : -1, high comp : 1
contrasts(d_critical_wide_cat_zScored$competence) <- contr.sum(2)
# low rel: -1, high rel: 1
contrasts(d_critical_wide_cat_zScored$relevance) <- contr.sum(2)
# leave main type dummy coded
contrasts(d_critical_wide_cat_zScored$main_type)

@@

```
```{r}
summary(model_xor_cat_zScored)
```
Now extract posterior contrasts of interest from categorical model: effects of each predictor \{prior, competence and relevance\} for each trigger.

@@

# check P that the effects are positive / negative / no effect present
posterior_hypotheses_cat <- model_xor_cat_zScored_posteriors %>% 
  select(prior_xor, prior_some, 
         competence_xor, competence_some,
         relevance_xor, relevance_some) %>%
  gather(key, val) %>%
  group_by(key) %>% mutate(positive = mean(val > 0.05),
                           negative = mean(val < -0.05),
                           no = mean(val %>% between(-0.05, 0.05))) %>%
  summarise(positive_eff = mean(positive),
            negative_eff = mean(negative),
            no_eff = mean(no))
posterior_hypotheses_cat
```

@@

#ggsave("../../writing/paper/images/posterior-effects-categorical.pdf", width=7, height=5)
```

Model with aggregated by-story ratings:
```{r, results='hide', message=FALSE, warning=FALSE}
d_critical_zScored_wide_byItem <- d_critical_zScored_wide %>% ungroup() %>%
  group_by(title, main_type) %>%
  summarize(mean_response = mean(target),
            mean_prior = mean(prior),
            mean_relevance = mean(relevance),
            mean_competence = mean(competence))

@@

# check P that the effects are positive / negative / no effect present
posterior_hypotheses_means <- model_means_posteriors %>% 
  select(prior_xor, prior_some, 
         competence_xor, competence_some,
         relevance_xor, relevance_some) %>%
  gather(key, val) %>%
  group_by(key) %>% mutate(positive = mean(val > 0.05),
                           negative = mean(val < -0.05),
                           no = mean(val %>% between(-0.05, 0.05))) %>%
  summarise(positive_eff = mean(positive),
            negative_eff = mean(negative),
            no_eff = mean(no))
posterior_hypotheses_means
```

@@

model_mean_posteriors_long %>%
  mutate(effect = factor(effect, 
                         levels = c("relevance_xor", "relevance_some", "prior_xor", "prior_some", "competence_xor", "competence_some"), 
                         labels = c("Relevance (or)", "Relevance (some)", "Prior (or)", "Prior (some)", "Competence (or)", "Competence (some)"))) %>%
  ggplot(.) + # 
  stat_halfeye(aes(y = effect, x = value, 
                   fill = stat(case_when(x %>% between(-0.05, 0.05) ~ "no effect", x < -0.05 ~ "negative effect", x > 0.05 ~ "positive effect"))
                   ), 
               alpha = .7) +
  geom_vline(xintercept = c(-.05, .05), linetype = "dashed") +
  scale_fill_manual(name = "Direction of effect", values = c("coral", "yellow3", "mediumseagreen")) +
  labs(x = "Effect size", y = "Effect") +
  theme(legend.position = "top",
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 12),
        axis.title = element_text(size = 13),
        strip.text.x = element_text(size = 13),
        strip.text.y = element_text(size = 13))

A non-preregistered, but nevertheless possibly interesting exploratory analysis including the two individual prior ratings of the conditionals in the xor condition as predictors (as opposed to the mean of the two used in the preceding models):
Analysis based on the order of appearance of the questions:
```{r, results='hide', message=FALSE, warning=FALSE}

>>>>

# add correctly filtered dataframes 
d_critical_noDuplicates_zScored <- read_csv("./../../data/main/results_prereg_tidy_noDuplicates_zScored_long.csv")
d_critical_noDuplicates_zScored_wide <- read_csv("./../../data/main/results_prereg_tidy_noDuplicates_zScored_wide.csv")
d_critical_noImplFails_noDuplicates_zScored <-
  read_csv("./../../data/main/results_prereg_tidy_noDuplicates_noImplFails_zScored_long.csv")
d_critical_noImplFails_noDuplicates_zScored_wide <-
  read_csv("./../../data/main/results_prereg_tidy_noDuplicates_noImplFails_zScored_wide.csv")

@@

Now perform the main confirmatory analysis on correctly z-scored data (no duplicates), to double-check that the results don't change qualitatively.
```{r, results='hide', message=FALSE, warning=FALSE}
# Full model 
d_critical_noDuplicates_zScored_wide <- d_critical_noDuplicates_zScored_wide %>% mutate(
  main_type = as.factor(main_type)
)
# some = 0, xor = 1
contrasts(d_critical_noDuplicates_zScored_wide$main_type)

model_SI_no_dupl <- brm(target ~ prior*competence*relevance* main_type +
                   (1 + prior + competence + relevance + main_type || submission_id) +
                   (1 | title),
                 data = d_critical_noDuplicates_zScored_wide,
                 prior = priors,
                 sample_prior = T,
                 control = list(adapt_delta = 0.95),
                 cores = 4,
                 iter = 3000)
```

```{r}
summary(model_SI_no_dupl)
```

Extract contrasts:
```{r}
model_SI_no_dupl %>% spread_draws(b_Intercept, b_prior, b_competence, b_relevance,
                          b_main_typexor, `b_prior:competence`,
                          `b_prior:relevance`, `b_competence:relevance`,
                          `b_prior:main_typexor`, `b_competence:main_typexor`,
                          `b_relevance:main_typexor`, `b_prior:competence:relevance`, 
                          `b_prior:competence:main_typexor`, `b_prior:relevance:main_typexor`,
                          `b_competence:relevance:main_typexor`, 
                          `b_prior:competence:relevance:main_typexor`) %>% 
  mutate(
    prior_xor = b_prior + `b_prior:main_typexor`,
    prior_some = b_prior,
    competence_xor = b_competence + `b_competence:main_typexor`,
    competence_some = b_competence,
    relevance_xor =  b_relevance + `b_relevance:main_typexor`,
    relevance_some = b_relevance
  ) -> model_SI_no_dupl_posteriors

# check P that the effects are positive / negative / no effect present
posterior_hypotheses_no_dupl <- model_SI_no_dupl_posteriors %>% 
  select(prior_xor, prior_some, 
         competence_xor, competence_some,
         relevance_xor, relevance_some) %>%
  gather(key, val) %>%
  group_by(key) %>% mutate(positive = mean(val > 0.05),
                           negative = mean(val < -0.05),
                           no = mean(val %>% between(-0.05, 0.05))) %>%
  summarise(negative_eff = mean(negative),
            no_eff = mean(no),
            positive_eff = mean(positive)
            )
posterior_hypotheses_no_dupl

# write out for reading values in paper
#posterior_hypotheses_no_dupl %>% write_csv("./../../writing/paper/data/posterior_h_confirmatory.csv")
```
Also check if the 0 ROPE results change on the correctly z-scored data:
```{r}
posterior_hypotheses_nullROPE_no_dupl <- model_SI_no_dupl_posteriors %>% 
  select(prior_xor, prior_some, 
         competence_xor, competence_some,
         relevance_xor, relevance_some) %>%
  gather(key, val) %>%
  group_by(key) %>% mutate(positive = mean(val > 0),
                           negative = mean(val < 0)) %>% # no = mean(val = 0)
  summarise(positive_eff = mean(positive),
            negative_eff = mean(negative) # no_eff = mean(no)
            )
posterior_hypotheses_nullROPE_no_dupl
#posterior_hypotheses_nullROPE_no_dupl %>% write_csv("./../../writing/paper/data/posterior_h_confirmatory_0-ROPE.csv")
```

Now investigate if the confirmatory results change if excluding participants who were resilient to contextual manipulations:
```{r, results='hide', message=FALSE, warning=FALSE}
# Full model 
d_critical_noImplFails_noDuplicates_zScored_wide <- d_critical_noImplFails_noDuplicates_zScored_wide %>% mutate(
  main_type = as.factor(main_type)
)
# some = 0, xor = 1
contrasts(d_critical_noImplFails_noDuplicates_zScored_wide$main_type)

model_SI_no_dupl_no_impl <- brm(target ~ prior*competence*relevance* main_type +
                   (1 + prior + competence + relevance + main_type || submission_id) +
                   (1 | title),
                 data = d_critical_noImplFails_noDuplicates_zScored_wide,
                 prior = priors,
                 sample_prior = T,
                 control = list(adapt_delta = 0.95),
                 cores = 4,
                 iter = 3000)
```

```{r}
summary(model_SI_no_dupl_no_impl)
```

Contrasts:
```{r}
model_SI_no_dupl_no_impl %>% spread_draws(b_Intercept, b_prior, b_competence, b_relevance,
                          b_main_typexor, `b_prior:competence`,
                          `b_prior:relevance`, `b_competence:relevance`,
                          `b_prior:main_typexor`, `b_competence:main_typexor`,
                          `b_relevance:main_typexor`, `b_prior:competence:relevance`, 
                          `b_prior:competence:main_typexor`, `b_prior:relevance:main_typexor`,
                          `b_competence:relevance:main_typexor`, 
                          `b_prior:competence:relevance:main_typexor`) %>% 
  mutate(
    prior_xor = b_prior + `b_prior:main_typexor`,
    prior_some = b_prior,
    competence_xor = b_competence + `b_competence:main_typexor`,
    competence_some = b_competence,
    relevance_xor =  b_relevance + `b_relevance:main_typexor`,
    relevance_some = b_relevance
  ) -> model_SI_no_dupl_no_impl_posteriors

# check P that the effects are positive / negative / no effect present
posterior_hypotheses_no_dupl_no_impl <- model_SI_no_dupl_no_impl_posteriors %>% 
  select(prior_xor, prior_some, 
         competence_xor, competence_some,
         relevance_xor, relevance_some) %>%
  gather(key, val) %>%
  group_by(key) %>% mutate(positive = mean(val > 0.05),
                           negative = mean(val < -0.05),
                           no = mean(val %>% between(-0.05, 0.05))) %>%
  summarise(positive_eff = mean(positive),
            negative_eff = mean(negative),
            no_eff = mean(no))
posterior_hypotheses_no_dupl_no_impl
```

0 ROPE:
```{r}
posterior_hypotheses_nullROPE_no_dupl_no_impl <- model_SI_no_dupl_no_impl_posteriors %>% 
  select(prior_xor, prior_some, 
         competence_xor, competence_some,
         relevance_xor, relevance_some) %>%
  gather(key, val) %>%
  group_by(key) %>% mutate(positive = mean(val > 0),
                           negative = mean(val < 0)) %>% # no = mean(val = 0)
  summarise(positive_eff = mean(positive),
            negative_eff = mean(negative) # no_eff = mean(no)
            )
posterior_hypotheses_nullROPE_no_dupl_no_impl
```

@@

The binary test of conformity with the theoretical predictions therefore is:
```{r}
test_conjunction_of_all_hypotheses <-  function(posterior_hypotheses) {
  posterior_hypotheses %>% 
    mutate(hypothesis_true = case_when(
      key == 'competence_some' ~ positive_eff > 0.95,
      key == 'competence_xor'  ~ positive_eff > 0.95,
      key == 'prior_some' ~ negative_eff > 0.95,
      key == 'prior_xor'  ~ negative_eff > 0.95, 
      key == 'relevance_some' ~ positive_eff > 0.95,
      key == 'relevance_xor'  ~ positive_eff > 0.95
    )) %>% 
    pull(hypothesis_true) %>% all()
}
# applied to the pilot data
test_conjunction_of_all_hypotheses(posterior_hypotheses)

# applied to correctly z-scored data
test_conjunction_of_all_hypotheses(posterior_hypotheses_no_dupl)
test_conjunction_of_all_hypotheses(posterior_hypotheses_no_dupl_no_impl)

```
### Plot posterior distributions

```{r, fig.height = 6, fig.width=9}
# model_SI_posteriors
model_SI_no_dupl_posteriors %>% select(prior_xor, prior_some,
                               competence_xor, competence_some,
                               relevance_xor, relevance_some) %>%
  pivot_longer(cols = everything(), names_to = "effect", values_to = "value") -> model_SI_posteriors_long

@@

#ggsave("../../writing/ELM2/posterior-effects.pdf", width=7, height=5)
#ggsave("../../writing/ELM2/posterior-effects-noDupl.pdf", width=7, height=5)
```

@@

Model with binary predictors:
```{r, results='hide', message=FALSE, warning=FALSE}
#d_critical_zScored %>% 
d_critical_noDuplicates_zScored %>%
  select(submission_id, title, main_type, response_centered, prior_class, class_condition, block_extended) %>% # ,
  unique() %>% 
  pivot_wider(
    names_from = class_condition, 
    values_from = prior_class
  )  -> d_critical_wide_cat_zScored

# wrangle prior categorization of the items for the correctly z-scored data 
d_critical_wide_cat_zScored %>%
  replace_na(list(relevance = 0, competence = 0, prior = 0)) %>%
  group_by(submission_id, title) %>%
  filter(block_extended != "target") %>%
  summarise_at(c( "relevance", "competence", "prior"), funs(sum)) %>%
  mutate(prior = ifelse(prior == 2, 1, prior)) -> d_critical_wide_cat_zScored_priors

d_critical_wide_cat_zScored_targets <- d_critical_wide_cat_zScored %>%
  select(submission_id, title, main_type, block_extended, response_centered) %>%
  filter(block_extended == "target") %>% select(-block_extended)

d_critical_wide_cat_zScored_full <- left_join(d_critical_wide_cat_zScored_priors, d_critical_wide_cat_zScored_targets, by = c("submission_id", "title") )

d_critical_wide_cat_zScored_full %>%
  mutate(relevance = factor(relevance, levels = c(1, 0)),
         competence = factor(competence, levels = c(1, 0)),
         prior = factor(prior, levels = c(1, 0)),
         main_type = as.factor(main_type)) -> d_critical_wide_cat_zScored #%>% 
#  filter(block_extended == "target") -> d_critical_wide_cat_zScored
# sum code predictors
# low prior: -1, high prior:: 1 
contrasts(d_critical_wide_cat_zScored$prior) <- contr.sum(2)
# low comp : -1, high comp : 1
contrasts(d_critical_wide_cat_zScored$competence) <- contr.sum(2)
# low rel: -1, high rel: 1
contrasts(d_critical_wide_cat_zScored$relevance) <- contr.sum(2)
# leave main type dummy coded
contrasts(d_critical_wide_cat_zScored$main_type)

@@

```{r}
summary(model_xor_cat_zScored)
```
Now extract posterior contrasts of interest from categorical model: effects of each predictor \{prior, competence and relevance\} for each trigger.

@@

# check P that the effects are positive / negative / no effect present
posterior_hypotheses_cat <- model_xor_cat_zScored_posteriors %>% 
  select(prior_xor, prior_some, 
         competence_xor, competence_some,
         relevance_xor, relevance_some) %>%
  gather(key, val) %>%
  group_by(key) %>% mutate(positive = mean(val > 0.05),
                           negative = mean(val < -0.05),
                           no = mean(val %>% between(-0.05, 0.05))) %>%
  summarise(positive_eff = mean(positive),
            negative_eff = mean(negative),
            no_eff = mean(no))
posterior_hypotheses_cat
#posterior_hypotheses_cat %>% write_csv("./../../writing/paper/data/posterior_h_exploratory_categorical.csv")
```

@@

#ggsave("../../writing/paper/images/posterior-effects-categorical.pdf", width=7, height=5)
#ggsave("../../writing/paper/images/posterior-effects-categorical-noDupl.pdf", width=7, height=5)
```

Model with aggregated by-story ratings:
```{r, results='hide', message=FALSE, warning=FALSE}
d_critical_zScored_wide_byItem <- d_critical_noDuplicates_zScored_wide %>% ungroup() %>%
  group_by(title, main_type) %>%
  summarize(mean_response = mean(target),
            mean_prior = mean(prior),
            mean_relevance = mean(relevance),
            mean_competence = mean(competence))

@@

# check P that the effects are positive / negative / no effect present
posterior_hypotheses_means <- model_means_posteriors %>% 
  select(prior_xor, prior_some, 
         competence_xor, competence_some,
         relevance_xor, relevance_some) %>%
  gather(key, val) %>%
  group_by(key) %>% mutate(positive = mean(val > 0.05),
                           negative = mean(val < -0.05),
                           no = mean(val %>% between(-0.05, 0.05))) %>%
  summarise(positive_eff = mean(positive),
            negative_eff = mean(negative),
            no_eff = mean(no))
posterior_hypotheses_means
#posterior_hypotheses_means %>% write_csv("./../../writing/paper/data/posterior_h_exploratory_means.csv")
```

@@

model_mean_posteriors_long %>%
  mutate(effect = factor(effect, 
                         levels = c("relevance_xor", "relevance_some", "prior_xor", "prior_some", "competence_xor", "competence_some"), 
                         labels = c("Relevance (or)", "Relevance (some)", "Prior (or)", "Prior (some)", "Competence (or)", "Competence (some)"))) %>%
  ggplot(.) + # 
  stat_halfeye(aes(y = effect, x = value, 
                   fill = stat(case_when(x %>% between(-0.05, 0.05) ~ "no effect", x < -0.05 ~ "negative effect", x > 0.05 ~ "positive effect"))
                   ), 
               alpha = .7) +
  geom_vline(xintercept = c(-.05, .05), linetype = "dashed") +
  scale_fill_manual(name = "Direction of effect", values = c("coral", "yellow3", "mediumseagreen")) +
  labs(x = "Effect size", y = "Effect") +
  theme(legend.position = "top",
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 12),
        axis.title = element_text(size = 13),
        strip.text.x = element_text(size = 13),
        strip.text.y = element_text(size = 13))
#ggsave("../../writing/paper/images/posterior-effects-means.pdf", width=7, height=5)
#ggsave("../../writing/paper/images/posterior-effects-means-noDupl.pdf", width=7, height=5)
```

[NOTE: Analyses below are not replicated on data z-scored correctly.]
A non-preregistered, but nevertheless possibly interesting exploratory analysis including the two individual prior ratings of the conditionals in the xor condition as predictors (as opposed to the mean of the two used in the preceding models):
Analysis based on the order of appearance of the questions:
```{r, results='hide', message=FALSE, warning=FALSE}
